---
title: "Notebook for interacting with Aircloak"
output: html_notebook
---

```{r}
library(ggplot2)
```

This notebook is a scaffold for querying Aircloak from R.

Since Aircloak Insights exposes a Postgres interface, you can query it using
the `RPostgreSQL` library (you might have to install it first).

```{r}
library("RPostgreSQL")

drv  <- dbDriver("PostgreSQL")
conn <- dbConnect(drv, dbname = "GamesAndPlayers",
                 host = "<HOST>", port = 5432,
                 user = "<USER>", 
                 password = "<PASSWORD>")
```

Which then allows you to query your database through Aircloak:

```{r}
ageDistribution <- dbGetQuery(conn, "SELECT age, count(*) FROM players GROUP BY age")
ggplot(data=ageDistribution, aes(x=age, y=count)) +
  geom_col() +  
  ylab("Number of players") +
  xlab("Age")
```

When working with sparse datasets, parts of your data might get anonymized away.
If the processing you are planning to do relies on the dataset being of a certain kind,
you might need to do further processing first, like omitting null values, and casting types:

```{r}
maxAgePerName <- dbGetQuery(conn, "
  SELECT lastname, max(age) as maxAge, count(distinct uid)
  FROM players 
  GROUP BY lastname
")
# Remove the entries where we do not have a max age
maxAgePerName <- na.omit(maxAgePerName)
# Only keep entries where we have more than 10 distinct users
maxAgePerName <- maxAgePerName[maxAgePerName$count > 10,]

# And now for some very scientific plotting of data
maxAgePerName$nameLength <- nchar(maxAgePerName$lastname)
ggplot(data=maxAgePerName, aes(x=nameLength, y=maxAge)) +
  geom_point() +
  geom_smooth() +
  ylab("Maximum age") + xlab("Name length")
```

